Seagrass mapping and monitoring \\ along the coasts of Crete, Greece

### 2011-02-17 MScDiplom_Lemenkova.tex
Comment 28 of Valentijn: updated Research Question 1

\paragraph{ANOVA-testing}\index[concepts]{Data!statistical analysis!ANOVA}
We applied \ac{ANOVA} (ANalysis Of Variance) testing for the analysis of the probability of the
spectral reflectance of \textit{P.oceanica} to be more or less spectrally distinct from other seafloor cover
types with changing depth. W are checking the statement Hypothesis $H_o$, is true, which is “the
spectral distinguishability of the seagrass \textit{P.oceanica} from other seafloor types is not changing with
varying \textit{in-situ} conditions, $H_o: \mu1 =\mu2 =\mu3=...= \mu n$, which gives the following outcome.
P(reject $H_o\mid H_o$ is valid)= P(X$>c\mid p$=.05).
where c comes for critical values and p=probability.
The result P=.05 is (Tab.\ref{tab:8}), hence, very small, which makes the statement of Hypothesis $H_o$ highly unlikely
(less than 1 in a 10 chance). The one-way \ac{ANOVA} highlighted a significant difference between data
of spectral reflectances of \textit{P.oceanica} at different depths (Tab.\ref{tab:9}), i.e. true is the opposite statement:
Hypothesis $H_a$=“the spectral discernibility of the seagrass \textit{P.oceanica} is distinctly changing, 
and seagrass can be spectrally discriminated from carbonate sand with varying \textit{in-situ} conditions,
 i.e. increasing depth, $H_o: \mu\neq\mu2\neq\mu3\neq ... \neq\mu n$.
As a result of the statistical testing, we came to the following conclusion.
The Hypothesis $H_a$ is true, which claims that the spectral discernibility of the seagrass \textit{P.oceanica} is
distinctly changing and can be discriminated from from other seafloor cover types (carbonate sand) with varying \textit{in-situ} conditions, 
i.e. increasing depth, $H_o: \mu1\neq\mu2\neq\mu3\neq...\neq\mu n$, which positively answers first research question.
Statistical results are illustrated with Error bars made using Excel's vertical box and Whisker Charts
(Box Plots).
The graphs were plotted on the basis of the following statistical data calculated from the sampling
measurements data: Table 2.

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.30]{Fig-30.jpg}
	\caption{\ac{WASI} water color spectral simulation modeller: \\ Spectral reflectance of \textit{P.oceanica} and silt at 0.5-4.0m. Pages: $<$\pageref{page-35}$>$, $<$\pageref{page-31}$>$, $<$\pageref{GUI}$>$}
	\label{fig:4.7}
\end{figure}

>>>>

\paragraph{ANOVA-testing}\index[concepts]{Data!statistical analysis!ANOVA}
We applied \ac{ANOVA} (ANalysis Of Variance) testing for the analysis of the probability of the
spectral reflectance of \textit{P.oceanica} to be more or less spectrally distinct from other seafloor cover
types with changing depth. W are checking the statement Hypothesis $H_o$, is true, which is “the
spectral distinguishability of the seagrass \textit{P.oceanica} from other seafloor types is not changing with
varying \textit{in-situ} conditions, $H_o: \mu1 =\mu2 =\mu3=...= \mu n$, which gives the following outcome.
P(reject $H_o\mid H_o$ is valid)= P(X$>c\mid p$=.05).
where c comes for critical values and p=probability.
The result P=.05 is (Tab.\ref{tab:8}), hence, very small, which makes the statement of Hypothesis $H_o$ highly unlikely
(less than 1 in a 10 chance). The one-way \ac{ANOVA} highlighted a significant difference between data
of spectral reflectances of \textit{P.oceanica} and carbonate sand at different depths, and and proved spectral discernibility of seagrass \textit{P.oceanica} from carbonate sand (Fig.\ref{fig:4.7})\label{firstq}, i.e. true is the opposite statement: Hypothesis $H_a$=“the spectral discernibility of the seagrass \textit{P.oceanica} is distinctly changing, 
and seagrass can be spectrally discriminated from carbonate sand with varying \textit{in-situ} conditions,
 i.e. increasing depth, $H_o: \mu\neq\mu2\neq\mu3\neq ... \neq\mu n$.
As a result of the statistical testing, we came to the following conclusion.
The Hypothesis $H_a$ is true, which claims that the spectral discernibility of the seagrass \textit{P.oceanica} is
distinctly changing and can be discriminated from from other seafloor cover types (carbonate sand) with varying \textit{in-situ} conditions, 
i.e. increasing depth, $H_o: \mu1\neq\mu2\neq\mu3\neq...\neq\mu n$, which positively answers first research question.
Statistical results are illustrated with Error bars made using Excel's vertical box and Whisker Charts (Box Plots).
The graphs were plotted on the basis of the following statistical data calculated from the sampling
measurements data: Table 2.

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.30]{Fig-30.jpg}
	\caption{Spectral reflectance of \textit{P.oceanica} and carbonate sand at different depths of 0.5-4.0m. \\ Modelled by \ac{WASI} water color spectral simulation. Pages: $<$\pageref{page-35}$>$, $<$\pageref{page-31}$>$, $<$\pageref{GUI}$>$, $<$\pageref{firstq}$>$}.
	\label{fig:4.7}
\end{figure}
